\documentclass[letterpaper,11pt]{article}
\usepackage{xcolor}
\definecolor{myColor1}{HTML}{000099}
\definecolor{myColor2}{HTML}{000044}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1
%-------------------------
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\classesList}[4]{\item\small{{#1 #2 #3 #4 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------
\begin{document}
\begin{center}
    {\Huge \scshape \textcolor{myColor1}{Ram Kadiyala}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ \textcolor{myColor2}{240-756-8427} ~ \href{mailto:rkadiyal@terpmail.umd.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{\textcolor{myColor2}{rkadiyal@terpmail.umd.edu}}} ~ 
    \href{https://linkedin.com/in/1024-m/}{\raisebox{-0.2\height}\faLinkedin\ \underline{\textcolor{myColor2}{linkedin.com/in/1024-m}}}  ~
    \href{https://github.com/1024-m}{\raisebox{-0.2\height}\faGithub\ \underline{\textcolor{myColor2}{github.com/1024-m}}} ~
    \href{https://www.rkadiyala.com}{\raisebox{-0.2\height}\faGlobe\ \underline{\textcolor{myColor2}{rkadiyala.com}}}
    \vspace{-10pt}
\end{center}
%-----------EDUCATION-----------
\section{\textcolor{myColor1}{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textcolor{myColor2}{University of Maryland , College Park}}{\textcolor{myColor2}{Aug 2022 -- May 2024}}
      {Masters in Machine Learning}{College Park, MD}\vspace{-4pt}
    \resumeSubheading
      {\textcolor{myColor2}{University of Maryland , College Park}}{\textcolor{myColor2}{Aug 2022 -- May 2023}}
      {Graduate Certificate in Data Science}{College Park, MD}\vspace{-4pt}
  \resumeSubHeadingListEnd
  \vspace{-16pt}
%-----------WORK EXPERIENCE-----------
%    \resumeSubheading
%      {Electronics Company}{May 2020 -- August 2020}
%      {Software Engineer Intern}{City, State}
\section{\textcolor{myColor1}{Work Experience}}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Research Assistant}} $|$ \emph{\textcolor{myColor2}{RVR\&JC}} \hfill \textbf{\textcolor{myColor2}{Jan 2024 -- May 2024}}}\vspace{-3pt}\\
      \vspace{10pt} Building models for automated annotation and classification of medical texts using LLMs for mental health applications.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Research Assistant}} $|$ \emph{\textcolor{myColor2}{VVIT}} \hfill \textbf{\textcolor{myColor2}{Aug 2023 -- Jan 2024}}}\vspace{-3pt}\\
      \vspace{10pt} Contributed in data pre-processing, and the development of ML models for more accurate glaucoma diagnosis.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Research Assistant}} $|$ \emph{\textcolor{myColor2}{RVR\&JC}} \hfill \textbf{\textcolor{myColor2}{Aug 2022 -- Jan 2023}}}\vspace{-3pt}\\
      \vspace{10pt} Assisted in building models for bias detection in Telugu news articles of each source in each domain to assist LLMs.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{IoT \& ML Intern}} $|$ \emph{\textcolor{myColor2}{Bolt IOT}} \hfill \textbf{\textcolor{myColor2}{Feb 2021 -- Apr 2021}}}\vspace{-5pt}\\
      \vspace{10pt} Contributed to a smart humidity, lighting, and temperature management project using programmable IoT devices.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Founder}} $|$ \emph{\textcolor{myColor2}{Black Ops Esports}} \hfill \textbf{\textcolor{myColor2}{Nov 2018 -- Apr 2022}}}\vspace{-5pt}\\
      \vspace{10pt} Established and led an E-sports organization, mentored teams across 14 games, managed the social handles and finances.\vspace{-10pt}
  \resumeSubHeadingListEnd 
%-----------PROGRAMMING SKILLS-----------
\section{\textcolor{myColor1}{Technical Skills}}
 \begin{itemize}[leftmargin=0.08in, label={}]
    \small{\item{
     \textbf{\textcolor{myColor2}{Languages}}{: Python, C, HTML/CSS, JavaScript, SQL, R, MATLAB, LaTeX} \\
     \textbf{\textcolor{myColor2}{Cloud Platforms}}{: Google Cloud Platform, Amazon Web Services} \\
     \textbf{\textcolor{myColor2}{Editing / Creative}}{: : Gradio, Prompt Engineering, SEO, UX Design, PhotoshopCC , AlightMotion, Google Sketchup} \\
    }}
 \end{itemize}
 \vspace{-21pt}  
%-----------CO-CURRICULAR ACHIEVEMENTS-----------
\section{\textcolor{myColor1}{Co-Curricular Achievements}}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{\textcolor{myColor2}{International Mathematics Olympiad 2015}}: Rank 283 out of over 700K\vspace{-5pt}}
    \resumeItem{\textbf{\textcolor{myColor2}{International Mathematics Olympiad 2014}}: Rank 183 out of over 650K\vspace{-5pt}}
    \resumeItem{\textbf{\textcolor{myColor2}{International Mathematics Olympiad 2013}}: Rank 389 out of over 650K\vspace{-5pt}}
    \resumeItem{\textbf{\textcolor{myColor2}{International Mathematics Olympiad 2012}}: Rank 110 out of over 650K\vspace{-8pt}}
  \resumeSubHeadingListEnd
%-----------PUBLICATIONS-----------
\section{\textcolor{myColor1}{Publications and Research}}
  \resumeSubHeadingListStart
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Multi-class Emotion detection on highly imbalanced data.}} \hfill\textbf{\textcolor{myColor2}{ACL 2023 (Published)}}}\\
        \vspace{6pt}  Devised a solution for detecting emotions from user essays on highly imbalanced data. Finished 1st out of 121 teams.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Word-Level Text Boundary Detection in Partially machine generated texts.}} \hfill\textbf{\textcolor{myColor2}{NAACL 2024 (Accepted)}}}\\
        \vspace{6pt}  Developed models to detect text boundary of LLM generated text in instruct variants of LLMs on data from unseen domains and LLMs. outperformed existing proprietary systems by 22 percent. Finished 1st out of 300+ teams.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Can LLMs Understand Social Media Texts Without Context ?}} \hfill\textbf{\textcolor{myColor2}{LREC-COLING 2024 (Under Review)}}}\\
        \vspace{6pt}  Developed models for classifying threat level and target groups in social media texts in low resource, code mixed languages.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Automated data collection, annotation and classification of medical texts using LLMs.}} \hfill\textbf{\textcolor{myColor2}{ACL 2024 (Ongoing)}}}\\
        \vspace{6pt}  Developing models for classification of medical text data through LLMs as a part of SMM4H 2024 Task 3,5,6.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Cross-lingual emotion and trigger span detection.}} \hfill\textbf{\textcolor{myColor2}{ACL 2024 (Ongoing)}}}\\
        \vspace{6pt}  Developing models to classify texts on emotion and detection of trigger text span through WASSA 2024 shared task 2.\vspace{-5pt}
    \resumeSubItem
      {\textbf{\textcolor{myColor2}{Multi-level Multi-modal Empathy Detection and Emotion Classification.}} \hfill\textbf{\textcolor{myColor2}{ACL 2024 (Ongoing)}}}\\
        \vspace{6pt}  Developing models to classify emotion and empathy in human-human, human-LLM chats through WASSA 2024 shared task 1.\vspace{-8pt}
  \resumeSubHeadingListEnd  
%-----------CERTIFICATIONS-----------
\section{\textcolor{myColor1}{Certifications}}
        \begin{multicols}{3}
            \begin{itemize}[itemsep=3pt, parsep=3pt]%\vspace{-20pt}
                \item\small \textcolor{myColor2}{Accelerated Computing - Nvidia}
                \item\small \textcolor{myColor2}{Data Analytics - Google}
                \item\small \textcolor{myColor2}{AWS Cloud essentials - Amazon}
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}  
%-----------PROJECTS-----------
\section{\textcolor{myColor1}{Other Projects}}
    \vspace{-7pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\textcolor{myColor2}{Tuneable Generative Image AI}} $|$ \emph{{PyTorch, Gradio, StableDiffusion, LoRA, Google Cloud Console}}}{}\vspace{-15pt}
          \vspace{-14pt}
      \resumeProjectHeading
          {\textbf{\textcolor{myColor2}{Power Outage Forecasting}} $|$ \emph{{RestAPI, FbProphet, Google Cloud, Anvil}}}{}\vspace{-15pt}
          \vspace{-14pt}
      \resumeProjectHeading
          {\textbf{\textcolor{myColor2}{Image/Video to Artistic Image/GIF Converter}} $|$ \emph{{CLIP, PixRay, Scipy, Pygame, PyTorch}}}{}\vspace{-15pt}
          \vspace{-14pt}
      \resumeProjectHeading
          {\textbf{\textcolor{myColor2}{LLM generated text detection}} $|$ \emph{{LLMs, Pytorch, CRF, AWS}}}{}\vspace{-15pt}
          \vspace{-14pt}    
      \resumeProjectHeading
          {\textbf{\textcolor{myColor2}{Sarcastic text generator reddit bot}} $|$ \emph{{LoRA, LLMs, Gradio, Google Cloud}}}{}\vspace{-15pt} 
    \resumeSubHeadingListEnd
\vspace{-14pt}
\end{document}